

    \filetitle{plotyy}{Line plot function with LHS and RHS axes for time series}{tseries/plotyy}

	\paragraph{Syntax}
 
 \begin{verbatim}
 [Ax,Lhs,Rhs,Range] = plotyy(X,Y,...)
 [Ax,Lhs,Rhs,Range] = plotyy(Range,X,Y,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{Range} {[} numeric {]} - Date range; if not specified the
   entire range of the input tseries object will be plotted.
 \item
   \texttt{X} {[} tseries {]} - Input tseries object whose columns will
   be plotted and labelled on the LHS.
 \item
   \texttt{Y} {[} tseries {]} - Input tseries object whose columns will
   be plotted and labelled on the RHS.
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{Ax} {[} handle \textbar{} numeric {]} - Handles to the LHS and
   RHS axes.
 \item
   \texttt{Lhs} {[} handle \textbar{} numeric {]} - Handles to series
   plotted on the LHS axis.
 \item
   \texttt{Rhs} {[} handle \textbar{} numeric {]} - Handles to series
   plotted on the RHS axis.
 \item
   \texttt{Range} {[} handle \textbar{} numeric {]} - Actually plotted
   date range.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'conincident='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Make the LHS and RHS y-axis grids
   coincident.
 \item
   \texttt{'dateFormat='} {[} char \textbar{}
   \emph{\texttt{irisget('plotDateFormat')}} {]} - Date format for the
   tick marks on the x-axis.
 \item
   \texttt{'dateTick='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
   Vector of dates locating tick marks on the x-axis; Inf means they will
   be created automatically.
 \item
   \texttt{'freqLetters='} {[} char \textbar{} \emph{\texttt{'YHQBM'}}
   {]} - Five letters to represent the five date frequencies (yearly,
   half-yearly, quarterly, bi-monthly, and monthly).
 \item
   \texttt{'lhsPlotFunc='} {[} \texttt{@area} \textbar{} \texttt{@bar}
   \textbar{} \emph{\texttt{@plot}} \textbar{} \texttt{@stem} {]} -
   Function that will be used to plot the LHS data.
 \item
   \texttt{'lhsTight='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Make the LHS y-axis tight.
 \item
   \texttt{'rhsPlotFunc='} {[} \texttt{@area} \textbar{} \texttt{@bar}
   \textbar{} \emph{\texttt{@plot}} \textbar{} \texttt{@stem} {]} -
   Function that will be used to plot the RHS data.
 \item
   \texttt{'rhsTight='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Make the RHS y-axis tight.
 \end{itemize}
 
 \paragraph{Description}
 
 \paragraph{Example}


