
    \foldertitle{SVAR}{Structural vector autoregressions: SVAR objects and functions}{SVAR/Contents}

	SVAR methods:

\paragraph{Constructor}\label{constructor}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{SVAR/SVAR}{\texttt{SVAR}} - Convert reduced-form VAR to
  structural VAR.
\end{itemize}

SVAR objects can call any of the \href{VAR/Contents}{VAR} functions. In
addition, the following functions are available for SVAR objects.

\paragraph{Getting information about SVAR
objects}\label{getting-information-about-svar-objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{SVAR/get}{\texttt{get}} - Query SVAR object properties.
\end{itemize}

\paragraph{Simulation}\label{simulation}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{SVAR/srf}{\texttt{srf}} - Shock (impulse) response function.
\end{itemize}

\paragraph{Stochastic properties}\label{stochastic-properties}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{SVAR/fevd}{\texttt{fevd}} - Forecast error variance
  decomposition for SVAR variables.
\end{itemize}

\paragraph{Manipulating SVAR objects}\label{manipulating-svar-objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{SVAR/sort}{\texttt{sort}} - Sort SVAR parameterisations by
  squared distance of shock reponses to median.
\end{itemize}

See help on \href{VAR/Contents}{VAR} objects for other functions
available.

\paragraph{Getting on-line help on SVAR
functions}\label{getting-on-line-help-on-svar-functions}

\begin{verbatim}
help SVAR
help SVAR/function_name
\end{verbatim}

\paragraph{Getting on-line help on SVAR functions that are inherited
from
VARs}\label{getting-on-line-help-on-svar-functions-that-are-inherited-from-vars}

\begin{verbatim}
help VAR
help VAR/function_name
\end{verbatim}



