

    \filetitle{arwm}{Adaptive random-walk Metropolis posterior simulator}{poster/arwm}

	\paragraph{Syntax}
 
 \begin{verbatim}
 [Theta,LogPost,AR,Scale,FinalCov] = arwm(Pos,NDraw,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{Pos} {[} poster {]} - Initialised posterior simulator object.
 \item
   \texttt{NDraw} {[} numeric {]} - Length of the chain not including
   burn-in.
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{Theta} {[} numeric {]} - MCMC chain with individual parameters
   in rows.
 \item
   \texttt{LogPost} {[} numeric {]} - Vector of log posterior density (up
   to a constant) in each draw.
 \item
   \texttt{AR} {[} numeric {]} - Vector of cumulative acceptance ratios
   in each draw.
 \item
   \texttt{Scale} {[} numeric {]} - Vector of proposal scale factors in
   each draw.
 \item
   \texttt{FinalCov} {[} numeric {]} - Final proposal covariance matrix;
   the final covariance matrix of the random walk step is
   Scale(end)\^{}2*FinalCov.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'adaptProposalCov='} {[} numeric \textbar{}
   \emph{\texttt{0.5}} {]} - Speed of adaptation of the Cholesky factor
   of the proposal covariance matrix towards the target acceptanace
   ratio, \texttt{targetAR}; zero means no adaptation.
 \item
   \texttt{'adaptScale='} {[} numeric \textbar{} \emph{\texttt{1}} {]} -
   Speed of adaptation of the scale factor to deviations of acceptance
   ratios from the target ratio, \texttt{targetAR}.
 \item
   \texttt{'burnin='} {[} numeric \textbar{} \emph{\texttt{0.10}} {]} -
   Number of burn-in draws entered either as a percentage of total draws
   (between 0 and 1) or directly as a number (integer greater that one).
   Burn-in draws will be added to the requested number of draws
   \texttt{ndraw} and discarded after the posterior simulation.
 \item
   \texttt{'estTime='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
   {]} - Display and update the estimated time to go in the command
   window.
 \item
   \texttt{'gamma='} {[} numeric \textbar{} \emph{\texttt{0.8}} {]} - The
   rate of decay at which the scale and/or the proposal covariance will
   be adapted with each new draw.
 \item
   \texttt{'initScale='} {[} numeric \textbar{} \texttt{1/3} {]} -
   Initial scale factor by which the initial proposal covariance will be
   multiplied; the initial value will be adapted to achieve the target
   acceptance ratio.
 \item
   \texttt{'progress='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Display progress bar in the command
   window.
 \end{itemize}
 
 *\texttt{'targetAR='} {[} numeric \textbar{} \emph{\texttt{0.234}} {]} -
 Target acceptance ratio.
 
 \paragraph{Description}
 
 Use the \url{poster/stats} function to process the raw chain produced by
 \texttt{arwm}.
 
 \paragraph{Example}


