

    \filetitle{regen}{Regeneration time MCMC Metropolis posterior simulator}{poster/regen}

	\paragraph{Syntax}\label{syntax}

\begin{verbatim}
[Theta,LogPost,AR,Scale,FinalCov] = regen(Pos,NDraw,...)
\end{verbatim}

\paragraph{Input arguments}\label{input-arguments}

\begin{itemize}
\item
  \texttt{Pos} {[} poster {]} - Initialised posterior simulator object.
\item
  \texttt{NDraw} {[} numeric {]} - Length of the chain not including
  burn-in.
\end{itemize}

\paragraph{Output arguments}\label{output-arguments}

\begin{itemize}
\item
  \texttt{Theta} {[} numeric {]} - MCMC chain with individual parameters
  in rows.
\item
  \texttt{LogPost} {[} numeric {]} - Vector of log posterior density (up
  to a constant) in each draw.
\item
  \texttt{AR} {[} numeric {]} - Vector of cumulative acceptance ratios
  in each draw.
\item
  \texttt{Scale} {[} numeric {]} - Vector of proposal scale factors in
  each draw.
\item
  \texttt{FinalCov} {[} numeric {]} - Final proposal covariance matrix;
  the final covariance matrix of the random walk step is
  \texttt{Scale(end)\^{}2*FinalCov}.
\end{itemize}

\paragraph{Options}\label{options}

\paragraph{References}\label{references}

\paragraph{Brockwell, A.E., and Kadane, J.B., 2004. ``Identification of
Regeneration Times in MCMC Simulation, with Application to Adaptive
Schemes,'' mimeo, Carnegie Mellon
University.}\label{brockwell-a.e.-and-kadane-j.b.-2004.-identification-of-regeneration-times-in-mcmc-simulation-with-application-to-adaptive-schemes-mimeo-carnegie-mellon-university.}

\paragraph{Example}\label{example}


