

    \filetitle{dat2str}{Convert IRIS dates to cell array of strings}{dates/dat2str}

	\paragraph{Syntax}
 
 \begin{verbatim}
 S = dat2str(Dat,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{Dat} {[} numeric {]} - IRIS serial date number(s).
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{S} {[} cellstr {]} - Cellstr with strings representing the
   input dates.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'dateFormat='} {[} char \textbar{} cellstr \textbar{}
   \emph{`YYYYFP'} {]} - Date format string, or array of format strings
   (possibly different for each date).
 \item
   \texttt{'freqLetters='} {[} char \textbar{} \emph{`YHQBM'} {]} -
   Letters representing the five possible frequencies
   (annual,semi-annual,quarterly,bimontly,monthly).
 \item
   \texttt{'months='} {[} cellstr \textbar{} \emph{English names of
   months} {]} - Cell array of twelve strings representing the names of
   months.
 \item
   \texttt{'standinMonth='} {[} numeric \textbar{} \texttt{'last'}
   \textbar{} \texttt{*1*} {]} - Which month will represent a
   lower-than-monthly-frequency date if month is part of the date format
   string.
 \end{itemize}
 
 \paragraph{Description}
 
 There are two types of date strings in IRIS: year-period strings and
 calendar date strings. The year-period strings can be printed for dates
 with yearly, half-yearly, quarterly, bimonthly, monthly, weekly, and
 indeterminate frequencies. The calendar date strings can be printed for
 dates with weekly and daily frequencies. Date formats for calendar date
 strings must start with a dollar sign, \texttt{\$}.
 
 \subparagraph{Year-period date strings}
 
 Regular date formats can include any combination of the following
 fields:
 
 \begin{itemize}
 \item
   \texttt{'Y'} - Year.
 \item
   \texttt{'YYYY'} - Four-digit year.
 \item
   \texttt{'YY'} - Two-digit year.
 \item
   \texttt{'P'} - Period within the year (half-year, quarter, bi-month,
   month, week).
 \item
   \texttt{'PP'} - Two-digit period within the year.
 \item
   \texttt{'R'} - Upper-case roman numeral for the period within the
   year.
 \item
   \texttt{'r'} - Lower-case roman numeral for the period within the
   year.
 \item
   \texttt{'M'} - Month numeral.
 \item
   \texttt{'MM'} - Two-digit month numeral.
 \item
   \texttt{'MMMM'}, \texttt{'Mmmm'}, \texttt{'mmmm'} - Case-sensitive
   name of month.
 \item
   \texttt{'MMM'}, \texttt{'Mmm'}, \texttt{'mmm'} - Case-sensitive
   three-letter abbreviation of month.
 \item
   \texttt{'Q'} - Upper-case roman numeral for the month or stand-in
   month.
 \item
   \texttt{'r'} - Lower-case roman numeral for the month or stand-in
   month.
 \item
   \texttt{'F'} - Upper-case letter representing the date frequency.
 \item
   \texttt{'f'} - Lower-case letter representing the date frequency.
 \item
   \texttt{'EE'} - Two-digit end-of-month day; stand-in month used for
   non-monthly dates.
 \item
   \texttt{'E'} - End-of-month day; stand-in month used for non-monthly
   dates.
 \item
   \texttt{'WW'} - Two-digit end-of-month workday; stand-in month used
   for non-monthly dates.
 \item
   \texttt{'W'} - End-of-month workday; stand-in month used for
   non-monthly dates.
 \end{itemize}
 
 \subparagraph{Calendar date strings}
 
 Calendar date formats must start with a dollar sign, \texttt{\$}, and
 can include any combination of the following fields:
 
 \begin{itemize}
 \item
   \texttt{'Y'} - Year.
 \item
   \texttt{'YYYY'} - Four-digit year.
 \item
   \texttt{'YY'} - Two-digit year.
 \item
   \texttt{'DD'} - Two-digit day numeral; daily and weekly dates only.
 \item
   \texttt{'D'} - Day numeral; daily and weekly dates only.
 \item
   \texttt{'M'} - Month numeral.
 \item
   \texttt{'MM'} - Two-digit month numeral.
 \item
   \texttt{'MMMM'}, \texttt{'Mmmm'}, \texttt{'mmmm'} - Case-sensitive
   name of month.
 \item
   \texttt{'MMM'}, \texttt{'Mmm'}, \texttt{'mmm'} - Case-sensitive
   three-letter abbreviation of month.
 \item
   \texttt{'Q'} - Upper-case roman numeral for the month.
 \item
   \texttt{'r'} - Lower-case roman numeral for the month.
 \item
   \texttt{'DD'} - Two-digit day numeral.
 \item
   \texttt{'D'} - Day numeral.
 \end{itemize}
 
 \subparagraph{Escaping control letters}
 
 To get the format letters printed literally in the date string, use a
 percent sign as an escape character: \texttt{'\%Y'}, \texttt{'\%P'},
 \texttt{'\%F'}, \texttt{'\%f'}, \texttt{'\%M'}, \texttt{'\%m'},
 \texttt{'\%R'}, \texttt{'\%r'}, \texttt{'\%Q'}, \texttt{'\%q'},
 \texttt{'\%D'}, \texttt{'\%E'}, \texttt{'\%D'}.
 
 \paragraph{Example}


