

    \filetitle{acf}{Autocovariance and autocorrelation functions for VAR variables}{VAR/acf}

	\paragraph{Syntax}\label{syntax}

\begin{verbatim}
[C,R] = acf(V,...)
\end{verbatim}

\paragraph{Input arguments}\label{input-arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{V} {[} VAR {]} - VAR object for which the ACF will be
  computed.
\end{itemize}

\paragraph{Output arguments}\label{output-arguments}

\begin{itemize}
\item
  \texttt{C} {[} namedmat \textbar{} numeric {]} - Auto/cross-covariance
  matrices.
\item
  \texttt{R} {[} namedmat \textbar{} numeric {]} -
  Auto/cross-correlation matrices.
\end{itemize}

\paragraph{Options}\label{options}

\begin{itemize}
\item
  \texttt{'applyTo='} {[} logical \textbar{} \emph{\texttt{Inf}} {]} -
  Logical index of variables to which the \texttt{'filter='} will be
  applied; the default Inf means all variables.
\item
  \texttt{'filter='} {[} char \textbar{} \emph{empty} {]} - Linear
  filter that is applied to variables specified by `applyto'.
\item
  \texttt{'matrixFmt='} {[} \emph{\texttt{'namedmat'}} \textbar{}
  \texttt{'plain'} {]} - Return matrices \texttt{C} and \texttt{R} as
  either \href{namedmat/Contents}{\texttt{namedmat}} objects
  (i.e.~matrices with named rows and columns) or plain numeric arrays.
\item
  \texttt{'nFreq='} {[} numeric \textbar{} \emph{\texttt{256}} {]} -
  Number of equally spaced frequencies over which the \texttt{'filter='}
  is numerically integrated.
\item
  \texttt{'order='} {[} numeric \textbar{} \emph{\texttt{0}} {]} - Order
  up to which ACF will be computed.
\item
  \texttt{'progress='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Display progress bar in the command
  window.
\end{itemize}

\paragraph{Description}\label{description}

\paragraph{Example}\label{example}


