

    \filetitle{userfigure}{Insert existing figure window}{report/userfigure}

	\paragraph{Syntax}\label{syntax}

\begin{verbatim}
P.userfigure(Caption,H,...)
\end{verbatim}

\paragraph{Input arguments}\label{input-arguments}

\begin{itemize}
\item
  \texttt{P} {[} struct {]} - Report object created by the
  \href{report/new}{\texttt{report.new}} function.
\item
  \texttt{Caption} {[} char \textbar{} cellstr {]} - Title or a cell
  array with title and subtitle displayed at the top of the figure; see
  Description for splitting the title or subtitle into multiple lines.
\item
  \texttt{H} {[} numeric {]} - Handle to a graphics figure created by
  the user that will be captured and inserted in the report.
\end{itemize}

\paragraph{Options}\label{options}

See help on \href{report/figure}{\texttt{report/figure}} for options
available.

\paragraph{Generic options}\label{generic-options}

See help on \href{report/Contents}{generic options} in report objects.

\paragraph{Description}\label{description}

The function \texttt{report/userfigure} inserts an existing figure
window (created by the user by standard Matlab commands, and referenced
by its handle, \texttt{H}) into a report:

\begin{itemize}
\item
  The figure and the graphs in it must be created \emph{before} you call
  \texttt{report/figure}: any changes or additions to the figure or its
  graphs made after you call the function will not show in the report.
\item
  The report figure cannot have any children; in other words, you cannot
  call \href{report/graph}{\texttt{report/graph}} after a call to
  \texttt{report/figure} with a graphics handle, \texttt{H}.
\end{itemize}

\subparagraph{Titles and subtitles}\label{titles-and-subtitles}

The input argument \texttt{Caption} can be either a text string, or a
1-by-2 cell array of strings. In the latter case, the first cell will be
printed as a title, and the second cell will be printed as a subtitle.

To split the title or subtitle into multiple lines, use the following
LaTeX commands wrapped in curly brackets:
\texttt{\{\textbackslash{}\textbackslash{}\}} or
\texttt{\{\textbackslash{}\textbackslash{}{[}Xpt{]}\}}, where \texttt{X}
is the width of an extra vertical space (in points) added between the
respective lines.

\paragraph{Example}\label{example}


